---
title: "2019-02-01_Heidebrink_SubjMem_MCI_AD"
author: "Nicolas May"
date: "2/6/2019"
output: 
  html_document:
    theme: cerulean
    highlight: espresso
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Requirements

## Load useful libraries

```{r}
library(dplyr)
```

## Load Useful Variables / Helpers

```{r}
source("~/Desktop/config.R")
source("~/Desktop/helpers.R")

# swith to access API (TRUE) or not (FALSE)
get_api_data <- TRUE
```

# Get Data

## Define UDS 3 data fields

```{r}
fields_u3_raw <- 
  c(
    "ptid"
    , "form_date"
    # ivp_b9
    , "decsub" # Does the subject report a decline in memory?
    # , "decin"  # Does the co-participant report a decline in subj's memory?
    # , "decclcog" # Clinix. judgment, is subj experiencing cognitive impair?
    # fvp_b9
    , "fu_decsub"
    # , "fu_decin"
    # , "fu_decclcog"
    # tvp_b9
    , "tele_decsub"
    # , "tele_decin"
    # , "tele_decclcog"
    # ivp_d1 
    , "normcog"  # normal cognition
    , "mciamem"  # aMCI SD
    , "mciaplus" # aMCI MD
    , "mcinon1"  # naMCI SD
    , "mcinon2"  # naMCI MD
    , "alzdis"   # Alz etiology
    , "alzdisif" # Alz etiology primary
    # fvp_d1 
    , "fu_normcog"
    , "fu_mciamem"
    , "fu_mciaplus"
    , "fu_mcinon1"
    , "fu_mcinon2"
    , "fu_alzdis"
    , "fu_alzdisif"
    # tvp_d1 
    , "tele_normcog"
    , "tele_mciamem"
    , "tele_mciaplus"
    , "tele_mcinon1"
    , "tele_mcinon2"
    , "tele_alzdis"
    , "tele_alzdisif"
  )

fields_u3 <- fields_u3_raw %>% paste(collapse = ",")
```

## Retrieve data via REDCap API

```{r}
if (get_api_data) {
  json_u3 <- rc_api_get(token = REDCAP_API_TOKEN_UDS3n,
                        fields = fields_u3)
}

df_u3 <- jsonlite::fromJSON(json_u3) %>% na_if("")
```

## Write raw data to CSV

```{r}
data.table::fwrite(df_u3, "df_u3.csv", na = "")
```


# Process Data

## Clean data

Filter out DDE entries.

```{r}
df_u3_cln <- df_u3 %>% 
  filter(str_detect(ptid, "^UM\\d{8}$"))
```

Filter out records with missing `form_date`s.

```{r}
df_u3_cln <- df_u3_cln %>% 
  filter(!is.na(form_date))
```

Collapse initial visit / follow-up visit / telephone visit fields.

```{r}
df_u3_cln <- collapse_ift_cols(df_u3_cln)
```

## Mutate data

Add `mci` yes/no, `alz_prim_etio` yes/no, `alz_scnd_etio` yes/no fields.

```{r}
df_u3_cln_mut <- df_u3_cln %>% 
  mutate(mci = case_when(
    normcog == 0L & 
      (mciamem == 1L | mciaplus == 1L | mcinon1 == 1L | mcinon2 == 1L) ~ 1L,
    TRUE ~ NA_integer_
  )) %>% 
  mutate(alz_prim_etio = case_when(
    alzdis == 1L & alzdisif == 1L ~ 1L,
    TRUE ~ NA_integer_
  )) %>% 
  mutate(alz_scnd_etio = case_when(
    alzdis == 1L & alzdisif == 2L ~ 1L,
    TRUE ~ NA_integer_
  ))
```

## Filter data

Get only most recent visits.

```{r}
df_u3_cln_mut_flt <- df_u3_cln_mut %>% 
  get_visit_n(id_field = ptid, date_field = form_date, n = Inf)
```

Get only those of interest:
1. MCI dx
2. AD etiology
3. Report memory decline

```{r}
df_u3_cln_mut_flt <- df_u3_cln_mut_flt %>% 
  filter(mci == 1L & 
           (alz_prim_etio == 1L | alz_scnd_etio == 1L) &
           decsub == 1L)
```


# Write to CSV

```{r}
data.table::fwrite(df_u3_cln_mut_flt, "df_u3_cln_mut_flt.csv", na = "")
```


```{r echo=FALSE}
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
